{\bf Affine.m} -- {\it Mathematica} package for Lie algebras of finite, affine and extended affine type

### 2011-04-08 AffineLieAlgebras/CPC/article.tex
Program summary template created

>>>>

{\footnotesize
\section*{Program summary}
\textit{Title of program:} Affine.m
\\
\textit{Catalogue identifier:}
\\
\textit{Program obtainable from:} (submitted to Computer Physics Communications) \\
%CPC Program Library, Queen's University of Belfast, N. Ireland. Also from
\mbox{}\qquad \texttt{http://github.com/naa/Articles/AffineLieAlgebras/Mathematica/}
\\
\textit{Reference in CPC to previous version:} 
\\
\textit{Catalogue identifier of previous version:}
\\
\textit{Does the new version supersede the original program?:}
\\
\textit{Computers:} Any computer running Mathematica
\\
\textit{Operating systems under which the new version has been
tested:} Linux, Unix, Windows XP, MacOS
\\
\textit{Programming language:} Mathematica (version 7.0 or higher)
\\
\textit{Memory required to execute with typical data:} 20 Mbyte
\\
\textit{No. of bits in a word:} 64 or 32
\\
\textit{No. of processors used:} 1
\\
\textit{No. of bytes in distributed program, including test data,
etc.:} 0.15 Mbyte
\\
\textit{Distribution format:} Unencoded compressed tar file
\\
\textit{Nature of physical problem:} 
TODO: Finite dimensional Lie algebras are important for physics. Affine for CFT/

Symmetry has been a very important fundamental principle under-
lying human knowledge about our physical world. Among several
mathematical formulations of symmetry, the Lie algebras and their
corresponding Lie groups are probably the ones most explored.
They were discovered by Sophus Lie and Wilhelm Killing during
the last two decades of the 19th century. Lie’s work on Lie groups
was inspired by Galois’ work in 1832 in which he discovered the
ﬁnite groups. Independently, Killing had started a classiﬁcation of
Lie groups which was the starting point to the Élie Cartan’s doctoral
thesis in the beginning at the 20th century. Cartan was able to make
a complete classiﬁcation of Lie groups. Since Cartan’s classiﬁca-
tion, the theory of Lie groups has been utilized in many branches
of physics, including molecular physics, atomic physics, nuclear
physics and particle physics.
\\
\textit{Method of solution:} The Butler-Portugal algorithm.
\\
\textit{Restrictions on the complexity of the problem:}
Calculations up to finite grade
\\
\textit{Typical running time:} A few seconds with generic expressions

%
}
